Proposal: Something Interesting

### 2023-10-09 proposal/proposal.tex
conclusion added

>>>>

\paragraph{Conclusion}
In conclusion, our study proposal describes a thorough and multi-methodological approach to investigate the effect of weather 
catastrophes on the pricing of home insurance policies and the development of methods to lessen the financial burden on homeowners. 
Our research attempts to provide important insights into this urgent topic by utilizing data from reliable sources including the 
Insurance Information Institute and Aon's 2023 Weather, Climate, and Catastrophe Insight Report. We will be able to present a 
comprehensive viewpoint on the topic and contribute to informed policy decisions and industrial practices thanks to the mix of 
statistical analysis, and data science approaches.
